---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# shinycsv

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Codecov test coverage](https://codecov.io/gh/LieberInstitute/shinycsv/branch/devel/graph/badge.svg)](https://codecov.io/gh/LieberInstitute/shinycsv?branch=devel)
[![R build status](https://github.com/LieberInstitute/shinycsv/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/LieberInstitute/shinycsv/actions)
[![GitHub issues](https://img.shields.io/github/issues/LieberInstitute/shinycsv)](https://github.com/LieberInstitute/shinycsv/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/LieberInstitute/shinycsv)](https://github.com/LieberInstitute/shinycsv/pulls)
[![DOI](https://zenodo.org/badge/72884509.svg)](https://zenodo.org/badge/latestdoi/72884509)
<!-- badges: end -->

This package allows interactive explorations of CSV files, data.frame objects stored in a Rdata file (only one data.frame stored), or other types of table files. You can view this shiny app deployed at [libd.shinyapps.io/shinycsv](https://libd.shinyapps.io/shinycsv/). If you are interested in the [showcase mode](http://shiny.rstudio.com/articles/display-modes.html), then check out [libd.shinyapps.io/shinycsv-showcase](https://libd.shinyapps.io/shinycsv-showcase/).

The vignette for this package is available at [LieberInstitute/shinycsv](http://Lieberinstitute.github.io/shinycsv/).

## Installation instructions

Get the latest stable `R` release from [CRAN](http://cran.r-project.org/). Then install `shinycsv` from [GitHub](https://github.com/LieberInstitute/shinycsv) with:

```{r 'install_dev', eval = FALSE}
BiocManager::install("LieberInstitute/shinycsv")
```

## Citation

Below is the citation output from using `citation('shinycsv')` in R. Please
run this yourself to check for any updates on how to cite __shinycsv__.

```{r 'citation', eval = requireNamespace('shinycsv')}
print(citation("shinycsv"), bibtex = TRUE)
```

Please note that the `shinycsv` was only made possible thanks to many other R and bioinformatics software authors, which are cited either in the vignettes and/or the paper(s) describing this package.

## Code of Conduct

Please note that the `shinycsv` project is released with a [Contributor Code of Conduct](http://bioconductor.org/about/code-of-conduct/). By contributing to this project, you agree to abide by its terms.

## Development tools

* Continuous code testing is possible thanks to [GitHub actions](https://www.tidyverse.org/blog/2020/04/usethis-1-6-0/)  through `r BiocStyle::CRANpkg('usethis')`, `r BiocStyle::CRANpkg('remotes')`, and `r BiocStyle::CRANpkg('rcmdcheck')` customized to use [Bioconductor's docker containers](https://www.bioconductor.org/help/docker/) and `r BiocStyle::Biocpkg('BiocCheck')`.
* Code coverage assessment is possible thanks to [codecov](https://codecov.io/gh) and `r BiocStyle::CRANpkg('covr')`.
* The [documentation website](http://LieberInstitute.github.io/shinycsv) is automatically updated thanks to `r BiocStyle::CRANpkg('pkgdown')`.
* The code is styled automatically thanks to `r BiocStyle::CRANpkg('styler')`.
* The documentation is formatted thanks to `r BiocStyle::CRANpkg('devtools')` and `r BiocStyle::CRANpkg('roxygen2')`.

For more details, check the `dev` directory.

This package was developed using `r BiocStyle::Biocpkg('biocthis')`.


